Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-02-27 paper.tex
Adding histograms and split plot
req event figure
Misc. edits

In this work we consider the dependence of plasmaspheric mass density in the \cite{Takahashi2010} in more detail in an attempt to identify the solar wind processes that drives changes in the plasma trough density.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{paperfigures/F107MD27d-GOES6.eps}
\includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
\caption{(a) 27-day averages of $F_{10.7}$ and $\rho_{eq}$. (b) Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
\caption{$D_{st}$ events from GOES 6. Upper panel: Events in the interval 1989-1991. Lower panel: Events in the interval 1983-1991.}
\label{DailyAverages}
\end{figure}

>>>>

In this work we consider the dependence of plasmaspheric mass density in the \cite{Takahashi2010} in more detail in an attempt to identify the solar wind processes that drives changes in the plasma trough density.  There are several issues that are addressed in detail: (1) the plasma density measurements are sparse and (2) the dependence on the north/south component of the solar wind magnetic field is expected to be nonlinear. For northward IMF, the plasmasphere can expand past geosynchronous orbit where measurements of density are made resulting in an increase in observed density; for southward IMF, events studies have shown an increase in density associated with strong southward IMF [\cite{Takahashi2010}; \cite{Yao2008}].  Issue (1) is addressed by considering \note{Finish}.  Issue (2) is addressed by considering epochs and linear correlations independent of the direction of the IMF and also by separation by averages of the northrward and southward IMF.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.40]{paperfigures/F107MD27d-GOES6.eps}
\includegraphics[scale=0.40]{paperfigures/ccplot-GOES6.eps}
\caption{Top: 27-day boxcar averages of $F_{10.7}$ and $\rho_{eq}$ from GOES 6. Bottom: Correlation between $\log(\rho_{eq})$ and $F_{10.7}$ using hour, day, and 27-day averaging intervals; compare to \cite{Takahashi2010} Fig.~14.}
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
\caption{$D_{st}$ events from GOES 6. Top: Events in the interval 1989-1991; compare to \cite{Takahashi2010} Fig.~11. Bottom: Events in the interval 1983-1991.}
\label{DailyAverages}
\end{figure}
